Reducing Acceptance Marks in Emerson-Lei Automata by QBF Solving

### 2023-06-05 paper/main.tex
last touch :-)

Table~\ref{tab:heatmap} shows the number of all automata constructed
from formulas from literature that have a given number of original
acceptance marks and a given number of acceptance marks after
multi-level reduction. The table indicates that in many cases only 1
or 2~marks can be saved. However, the achieved reduction is
substantial for some automata with a higher number of original
acceptance marks. For example, in 26 cases, we have reduced 7 or more
acceptance marks to only 4 or less.
% Moreover, there were many timeouts of the last QBF query for manof these automata.
% Let us note that some that some reductions are the results are promising, e.g. in 17 cases, we have successfully
% reduced 8 or more acceptance marks to only 4.
Table~\ref{tab:heatmap-random} shows the same information for all
automata constructed from random formulas.

\begin{table}[t]
  \caption{The effect of multi-level reduction on automata constructed
    from formulas from literature.  A cell on coordinates $(x,y)$
    contains the number of automata that have been reduced from $x$ to
    $y$ acceptance marks. If the cell contains a sum of two numbers,
    the latter represents the number of automata where the attempt to
    reduce another mark has been unsuccessful due to a QBF solver
    timeout.}
\label{tab:heatmap}
\setlength{\tabcolsep}{2.5pt}
\centering
\input{table-heatmap.tex}
\end{table}

\begin{table}[t]
\caption{The effect of multi-level reduction on automata constructed
    from random formulas. The meaning of each cell is the same as in Table~\ref{tab:heatmap}.}
\label{tab:heatmap-random}
\setlength{\tabcolsep}{2.5pt}
\centering
\input{table-heatmap-random.tex}
\end{table}

>>>>

Table~\ref{tab:heatmap} shows the effect of multi-level reduction to
the number of acceptance marks in individual automata constructed from
formulas from literature.
% that have a given number of original
% acceptance marks and a given number of acceptance marks after
% multi-level reduction.
The table indicates that in many cases only 1 or 2~marks can be
saved. However, the achieved reduction is substantial for some
automata with a higher number of original acceptance marks. For
example, in 26 cases, we have reduced 7 or more acceptance marks to
only 4 or less.
% Moreover, there were many timeouts of the last QBF query for manof these automata.
% Let us note that some that some reductions are the results are promising, e.g. in 17 cases, we have successfully
% reduced 8 or more acceptance marks to only 4.
Table~\ref{tab:heatmap-random} shows the same information for
automata constructed from random formulas.

\begin{table}[t]
  \caption{The effect of multi-level reduction on all considered
    automata constructed from formulas from literature.  A cell on
    coordinates $(x,y)$ contains the number of automata that have been
    reduced from $x$ to $y$ acceptance marks. If the cell contains a
    sum of two numbers, the latter represents the number of automata
    where the attempt to reduce another mark has been unsuccessful due
    to a QBF solver timeout.}
\label{tab:heatmap}
\setlength{\tabcolsep}{2.5pt}
\centering
\input{table-heatmap.tex}
\end{table}

\begin{table}[t]
  \caption{The effect of multi-level reduction on all considered
    automata constructed from random formulas. The meaning of each
    cell is the same as in Table~\ref{tab:heatmap}.}
\label{tab:heatmap-random}
\setlength{\tabcolsep}{2.5pt}
\centering
\input{table-heatmap-random.tex}
\end{table}
